Designing Types for R, Empirically

### 2020-05-16 paper/main.tex
minor

First we look at the share of monomorphic arguments and function signatures.
Monomorphic in this context means that the type is not relying on \any or
including a union.  The import of monorphism in this context is that it
means our type language can accurately capture an argument's type or a
function signature.

@@

Figure~\ref{fig:unionfreq} shows the number of types inferred at each position of a
function signature. Most functions admit or return a uni-typed value. There are
\PercUnitypedPositions uni-typed parameter and return value positions in
function signatures. Only \PercManytypedPositions positions have more than three
types ascribed to them.

\input{tables/uni-typed-breakdown.tex}
Table~\ref{fig:singlefreq} provides a breakdown of the different type categories
observed at uni-typed positions. Scalar, class and vector are
the most common type categories. The shaded rows correspond to polymorphic
types. Removing those gives us \CountMonomorphicPositions
(\PercMonomorphicPositions) monomorphic positions in a corpus of \CountPositions
parameter and return positions.

>>>>

First we look at the share of monomorphic arguments and function signatures.
Monomorphic in this context means that the type is not relying on \any or
including a union.  The import of monorphism in this context is that it
means our type language can accurately capture an argument's type or a
function signature. We get to that number in two steps.
Fig.~\ref{fig:unionfreq} shows the number of inferred argument types and
their size (in terms of terms in the union). The figure shows the most
functions do not require a union at all (\PercUnitypedPositions of arguments
do not have a union), and only \PercManytypedPositions positions have unions
with more than three members.

@@

\input{tables/uni-typed-breakdown.tex}

Table~\ref{fig:singlefreq} provides a breakdown of the different type
categories observed at uni-typed positions. Scalar, class and vector are the
most common type categories. The shaded rows correspond to polymorphic
types. Removing those gives us \CountMonomorphicPositions
(\PercMonomorphicPositions) monomorphic positions in a corpus of
\CountPositions parameter and return positions.
